CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-03 paper_I/ms.tex
update paper

The clusters with the largest claimed numbers of sources are the
Platais~6, Platais~5, and Mamajek~3 moving groups, all from
\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
respectively. These membership claims should be regarded with some
skepticism on a source-by-source basis.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (= 32$\,$Ori) has only about 50 confirmed members
\citep{bell_32ori_2017}.

@@

@@

>>>>

Table~\ref{tbl:s6_lcs} shows the clusters with the largest claimed 
numbers of sources. The top 4 are all moving groups or stellar
associations from
\citet{dias_proper_2014}: Platais~5, Platais~6, Mamajek~, and Collinder~70.
These membership claims should be regarded with serious
skepticism on a source-by-source basis.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
\citep{bell_32ori_2017}.

@@

\section{Discussion}
\label{sec: discussion}

Despite our goal of completeness, some clusters may still be missing
members~--~the census of nearby coeval stellar populations is still
very much in flux ({\it e.g.}, \citealt{sim_open_2019};
\citealt{kounkel_untangling_2019}).  One particular area for concern in
the present work is sub-clusters of broader star-forming complexes,
for instance the Orion Nebula (M42; NGC 1976).  While it was observed
by TESS in Sector~6, searching our light curves for stars within 40
arcminutes, and 100 parsecs of the Orion Nebula's center yielded only
180 light curves, with 85 labelled members.  The Orion Nebula has
thousands of known members \citep{jones_proper_1988}.  However, due to
a combination of the spatially distributed nature of the broader
complex, as well as differential extinction, the automated methods of
the \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}
assigned the Orion Nebula only 44 and 326 members, respectively.
\citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
regions from their search, since the underlying assumption of their
clustering method (uniformity in the field star distribution) breaks
down in highly clustered star-forming regions.

@@

\begin{deluxetable}{lll}
	\tablecaption{Counts of light curves per cluster in Sector 6, sorted
		in descending order.  \label{tbl:s6_lcs}}
	\tablenum{2}

	\tablehead{
		\colhead{\hspace{.9cm}Name}\hspace{.9cm}
		& \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
		& \colhead{\hspace{.9cm}Description}\hspace{.2cm}
	}

	\startdata
	\input{table_s6_most_common_clusters.tex}
	\enddata

	\tablecomments{
		Table~\ref{tbl:s6_lcs} is published in its entirety in a machine-readable format.
		A portion is shown here for guidance regarding its form and content.
		Names are matched against \citet{Kharchenko_et_al_2013} as
		described in Appendix~\ref{appendix:uniquenames}, and $N_{\rm lc}$
		is the number of light curves associated with the cluster from this
		data release.
		The description column matches \citet{Kharchenko_et_al_2013},
		and is in the format ``\texttt{a},\texttt{b},\texttt{c},\texttt{d}''.
		Meanings of displayed symbols are as follows.
		\texttt{a}:
		``='' = cluster parameters were determined,
		``\&'' = duplicated/coincides with other cluster;
		\texttt{b}:
		``blank'' = open cluster,
		``a'' =	association,
		``m'' =	moving group,
		``n'' =	nebulosity;
		\texttt{c}:
		``o'' = object,
		``c'' = candidate;
		\texttt{d}:
		``ass'' =	stellar association,
		``var'' =	clusters with variable extinction.
	}

	\vspace{-1cm}
\end{deluxetable}

\begin{deluxetable}{lll}
	\tablecaption{Counts of light curves per cluster in Sector 7, sorted
		in descending order.  \label{tbl:s7_lcs}}
	\tablenum{3}

	\tablehead{
		\colhead{\hspace{.9cm}Name}\hspace{.9cm}
		& \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
		& \colhead{\hspace{.9cm}Description}\hspace{.2cm}
	}

	\startdata
	\input{table_s7_most_common_clusters.tex}
	\enddata

	\tablecomments{
		Table~\ref{tbl:s7_lcs} is published in its entirety in a machine-readable format.
		A portion is shown here for guidance regarding its form and content.
		Format is same as Table~\ref{tbl:s6_lcs}.
	}

	\vspace{-1cm}
\end{deluxetable}
